Supplementary Materials for \"COATi: statistical pairwise alignment of protein coding sequences\

### 2024-01-29 alignpair_letter.tex
Update colorblind colors.
Add new figure projecting the distance between aligners in 2d space

@@

>>>>

\begin{figure}[h!]
    \centering%
    \includegraphics{figures/fig-dseq-benchmarks.pdf}
    \par
    \caption{COATi's alignments were closer to the semi-empirical benchmark than other methods. A principal coordinates analysis of the average alignment distance ($d_{seq}$) between alignments generated by different methods. Not only were COATi's alignments on average closest to the benchmark, but other aligners tended to diverge from the benchmark in different directions.
%
    \label{fig:dseq-benchmarks}}
\end{figure}

@@

% NOTES:
% - Benchmark only contains seqeunces with gaps, which will make alignes look more different than they are in practice
% - Parameters and optimization
% - simulalation contained a lot of frameshifts that produed stop codons. Probably too many.
% - redo colors of figures 1 - 3.
% - define an equivalent alignment again in the benchmark results
